Thread Pool in GeckoDB/BOLSTER

### 2018-05-14 Presentations/Milestone2/presentation.tex
small corrections
Add wait for task id slide

\section{Concept and Design}
\begin{frame}
	\frametitle{Concept}
	\begin{itemize}
		\item Thread pool with runtime fixed amount of threads and lock free priority queue
		\item Tasks are not preemtable and independent
		\item Array of tasks passed to an enqueue function, which waits until all tasks are finished
		\item Threads without tasks idle until they get a new one
		\item Monitoring/managing state and assigned task of each thread
		\item Allow usage of multiple, independent thread pool instances 
	\end{itemize}
\end{frame}

@@

\section{Current Progress}
\begin{frame}
	\frametitle{Current Progress}
	We...
	\begin{itemize}
		\item Implemented the lock free priority queue 
		\item Implemented the creation of threads and the assigning of tasks
		\item Added gtest framework to project and wrote tests for pool and queue
		\item Began first implementations of waiting for tasks to be finished
		\item Measure performance of task assigning and execution
	\end{itemize}
\end{frame}

\section{Next Steps}
\begin{frame}
	\frametitle{Next Steps}
	We have to ...
	\begin{itemize}
		\item Find an efficient way ton wait for tasks
		\item Find an efficient way to idle threads until they get the next tasks
		\item Add metrics to threads and tasks and measure performance and overhead
		\item Add tests for all implementations
	\end{itemize}
\end{frame}

@@

\section{Additional Literature Research}
    \begin{frame}
        \frametitle{Additional Literature Research}
        \begin{itemize}
            \item Albahari, Joseph. \emph{Threading in C.} online. Joseph Albahari \& O’Reilly Media, Inc (2006).
            \item Rasmussen, Rasmus V., and Michael A. Trick. \emph{Round robin scheduling–a survey.} European Journal of Operational Research 188.3 (2008): 617-636.
            \item Shreedhar, Madhavapeddi, and George Varghese. \emph{Efficient fair queueing using deficit round robin.} ACM SIGCOMM Computer Communication Review. Vol. 25. No. 4. ACM, 1995.
        \end{itemize}
    \end{frame}

>>>>

\section{Concept and Design}
\begin{frame}
	\frametitle{Concept}
	\begin{itemize}
		\item Thread pool with runtime dynamic amount of threads and priority queue
		\item Tasks are not preemtable and independent
		\item Array of tasks passed to an enqueue function, which waits until all tasks are finished
		\item Threads without tasks idle until they get a new one
		\item Monitoring/managing state and assigned task of each thread
		\item Allow usage of multiple, independent thread pool instances 
	\end{itemize}
\end{frame}

@@

\section{Current Progress}
\begin{frame}
	\frametitle{Current Progress}
	We...
	\begin{itemize}
		\item Implemented the priority queue 
		\item Implemented the creation of threads and the assigning of tasks
		\item Added gtest framework to project and wrote tests for pool and queue
		\item Began first implementations of waiting for tasks to be finished
		\item Measure performance of task assigning and execution
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{Wait for task ID - Problem}
	\begin{itemize}
		\item Problem: waiting for a task to complete could lead to a
			race condition
		\item This was caused by the uncertainty of a thread\_task
			during transition between the priority queue and the
			thread pool
		\item Solution: Threads now increase an atomic counter
	\end{itemize}
\end{frame}

\section{Next Steps}
\begin{frame}
	\frametitle{Next Steps}
	We have to ...
	\begin{itemize}
		\item Find an efficient way to wait for tasks
		\item Find an efficient way to idle threads until they get the next tasks
		\item Add metrics to threads and tasks and measure performance and overhead
		\item Add tests for all implementations
	\end{itemize}
\end{frame}

@@

\section{Additional Literature Research}
    \begin{frame}
        \frametitle{Additional Literature Research}
        \begin{itemize}
            \item Albahari, Joseph. \emph{Threading in C\#.} online. Joseph Albahari \& O’Reilly Media, Inc (2006).
            \item Rasmussen, Rasmus V., and Michael A. Trick. \emph{Round robin scheduling–a survey.} European Journal of Operational Research 188.3 (2008): 617-636.
            \item Shreedhar, Madhavapeddi, and George Varghese. \emph{Efficient fair queueing using deficit round robin.} ACM SIGCOMM Computer Communication Review. Vol. 25. No. 4. ACM, 1995.
        \end{itemize}
    \end{frame}
